---
title: "Untitled"
output: github_document
---

# Artificial Intelligence and Energy

Before we begin, we need to import the relevant datasets, here is one for the energy consumption:
```{r}
energy <- read.csv("energy_data.csv")
head(energy)
```

...and here is one for AI patents:

```{r}
patent <- read.csv("ai_patents.csv")
head(patent)
```

Obviously, we need to merge them in some way. This is what we have done.

```{r}
library(dplyr)
energy <- energy %>% filter(iso_code != "") %>% group_by(country, year) %>% mutate(combinekey = paste(iso_code,toString(year)))
patent <- patent %>% group_by(Code, Year) %>% mutate(combinekey = paste(Code,toString(Year)))
combine <- inner_join(patent, energy, by = c("combinekey"))
head(combine)
```

In summary, what we have done is as follows:
- Only considered countries with an ISO code (meaning no regionals)
- Merged the data between the energy consumption and the patent data for each country and each year

Of course, we can do further consolidation as we go along.

**A warning about our observations**

Specifically, we ARE looking at an unbalanced dataset.

```{r}
combine %>% group_by(Code) %>% count(Code)
combine %>% group_by(Year) %>% count(Year)
```